\clearpage
\noindent\textit{Title:}\\
\textbf{Connections on Differentiable Manifolds}\\[0.25cm]
\textit{Author:} Martin Šimák\\[0.25cm]
\textit{Study programme:} Open Electronic Systems\\[0.25cm]
\textit{Supervisor:} doc. RNDr. Jiří Velebil, Ph.D., Department of Mathematics FEE\\[0.25cm]
\textit{Abstract:}\\
One of the aims of this thesis is to fully introduce a comprehensive differentiable structure on a smooth manifold. To achieve that, we first inspect various aspects of its definition. Further, we introduce a tangent structure on said manifolds, allowing us to locally speak of derivatives and vector fields. This construction naturally results in definitions of a covariant derivative and a connection form, where the former serves as a generalization of a derivative in a direction and the latter as a tool for ``glueing'' tangent spaces together. As a climax of the thesis, we show that the two previously mentioned additional structures on the ambient manifold are equivalent.\\[0.25cm]
\textit{Keywords:} smooth manifolds, tangent structure, covariant derivative, connection\\[0.5cm]
\noindent\textit{Název práce:}\\
\textbf{Konexe na diferencovatelných varietách}\\[0.25cm]
\textit{Autor:} Martin Šimák\\[0.25cm]
\textit{Studijní program:} Otevřené elektronické systémy\\[0.25cm]
\textit{Vedoucí:} doc. RNDr. Jiří Velebil, Ph.D., katedra matematiky FEL\\[0.25cm]
\textit{Abstrakt:}\\
\foreignlanguage{czech}{Jedním z cílů této práce je v plném měřítku uvést rozsáhlou diferenciální strukturu na hladké varietě. Abychom toho dosáhli, prozkoumáme nejprve jednotlivé aspekty její definice. Dále na varietách uvedeme tečnou strukturu, jenž nám umožňuje lokálně hovořit o derivacích a vektorových polích. Tato konstrukce přirozeně vyúsťuje v definice kovariantní derivace a konexe, přičemž první z pojmů slouží jakožto zobecnění derivace ve směru a druhý jakožto nástroj pro \uv{slepování} tečných prostorů. Jako vyvrcholení práce ukážeme, že tyto dvě dodatečné struktury na varietě jsou ekvivalentní.}\\[0.25cm]
\textit{Klíčová slova:} hladké variety, tečná struktura, kovariantní derivace, konexe\\[0.5cm]
\clearpage