\clearpage
\vspace*{\fill}
\noindent\textbf{Acknowledgements}\\[0.25cm]
Above all, I would like to thank my supervisor, doc. Ing. Pavel Hazdra, Ph.D., for his professional help, willingness, and reliable correspondence throughout our collaboration, which took place remotely during my double degree program in cooperation with the National Taiwan University of Science and Technology. I would also like to thank my supervisor, Ding-Bing Lin, who is responsible for the content of this thesis at the partner university, for his initiative and valuable assistance, especially in the design production. Last but not least, I would like to thank all my loved ones who supported me from afar throughout my studies, especially my family and friends. Special thanks go to Ester \foreignlanguage{czech}{Jančaříková} for standing by me and helping me through difficult times.\\
\hrule\vspace*{1cm}
\begin{otherlanguage}{czech}
    \noindent\textbf{Poděkování}\\[0.25cm]
    Především bych rád poděkoval svému vedoucímu, doc. Ing. Pavlu Hazdrovi, Ph.D., za jeho odbornou pomoc, vstřícnost, a ochotu v podobě spolehlivé korespondence během spolupráce, která probíhala distančně v rámci mého studia double degree programu ve spolupráci s National Taiwan University of Science and Technology. Dále děkuji svému vedoucímu Ding-Bing Linovi, který odpovídá za náplň této práce na partnerské univerzitě, za jeho iniciativu a cennou pomoc, zejména při výrobě návrhu. V neposlední řadě bych rád poděkoval všem svým blízkým, kteří mě na dálku podporovali během celého studia, zejména své rodině a přátelům. Zvláštní poděkování na závěr potom patří Ester Jančaříkové za to, že stála při mě a byla mi oporou v nelehkých chvílích.
\end{otherlanguage}
\clearpage